\documentclass[a4paper,11pt]{article}
\usepackage{fontawesome5}

\usepackage[backend=bibtex,maxnames=10,sorting=ydnt,defernumbers=true,doi=false,isbn=false,style=trad-abbrv]{biblatex}
\addbibresource{cv.bib}

\DeclareBibliographyCategory{starred}
\addtocategory{starred}{Chamon23c, Robey21a, Chamon20f, Eisen19l, Paternain19c}

\defbibenvironment{bibliography}{%
\list
{\ifcategory{starred}{\makebox[0pt][r]{\raisebox{1.2pt}{\tiny\faStar}~~}}{}%
\printtext[labelnumberwidth]{\printfield{labelprefix}\printfield{labelnumber}}}
{\setlength{\parskip}{0pt}
\setlength{\itemsep}{3pt}
\setlength{\parsep}{\bibparsep}
\setlength{\labelsep}{\biblabelsep}
}
}{\endlist}
{\item}


%-----------------------------------------------------------
\usepackage[paper=letterpaper, margin=1in]{geometry}
\usepackage{fancyhdr}

\fancypagestyle{LFOCheader}{%
	\fancyhf{} % clear all header and footer fields
	\fancyfoot[RO,RE]{\small\thepage}
	\fancyfoot[LO,LE]{\textsc{Luiz F.\ O.\ Chamon}}
	\renewcommand{\headrulewidth}{0pt}
	\renewcommand{\footrulewidth}{0pt}
}
\pagestyle{LFOCheader}

% Delete this if not using colors or links!
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{bluelink}{rgb}{0.1,0.2,0.7}

\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=bluelink
}
\urlstyle{same}


\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\pagestyle{empty}
\def\refname{}

% Define the heading style
\makeatletter
\def\NMSB@styleCV#1#2{%
	\vspace{5mm}%
	\vbox{\CVheading{#1#2}}%
	\vspace{2mm}%
}
\makeatother

%-----------------------------------------------------------
%Custom commands
\newcommand{\CVheader}[4]{
	\begin{tabular*}{\textwidth}{lr}
		\multicolumn{2}{l}{{\Huge \textsc{#1}} \vspace{1mm}}
		\\
		\begin{minipage}{0.5\textwidth}
			\href{#3}{#4}
		\end{minipage}
		&
		\begin{minipage}{0.5\textwidth}
			\flushright \href{mailto:#2}{#2}
		\end{minipage}
		\\
	\end{tabular*} \\ \vspace{1mm}
}


\newcommand{\CVheading}[1]{
	\vspace{10pt}
	{ \large
	\begin{minipage}{\textwidth}
		\textsc{#1 \vphantom{p\^{E}}}
	\end{minipage} } \\
	\vspace{5pt}
}


\newcommand{\CVsubheading}[2]{
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
	\end{tabular*} \\
}


\newcommand{\CVlist}{
	\begin{list}{$\bullet$}{
	\setlength{\itemsep}{0pt}
	\setlength{\parsep}{1pt}
	\setlength{\topsep}{1pt}
	\setlength{\partopsep}{0pt}
	\setlength{\leftmargin}{24pt}
	\setlength{\labelwidth}{1em} }
}


\newcommand{\CVlistend}{
	\end{list}
	\vspace{3pt}
}


%-----------------------------------------------------------

\begin{document}

\CVheader%
{Luiz F. O. Chamon}%
{luiz.chamon@simtech.uni-stuttgart.de}%
{https://www.luizchamon.com}{https://www.luizchamon.com}




%%%%%%%%%%%%%%%%%%%%%%
\CVheading{Positions}

\CVsubheading{University of Stuttgart---Germany}{2022--present}
\textit{Independent research group leader (ELLIS--SimTech)}
\vspace{3pt}


\CVsubheading{University of California, Berkeley---USA}{2021--2022}
\textit{Postdoctoral fellow at the Simons Institute for the Theory of Computing}
\vspace{3pt}

\CVsubheading{University of Pennsylvania---USA}{2020--2021}
\textit{Postdoctoral researcher}
\vspace{3pt}


%%%%%%%%%%%%%%%%%%%%%%
\CVheading{Education}

\CVsubheading{University of Pennsylvania---USA}{2015--2020}
\textit{Ph.D.\ in Electrical Engineering}

	\CVlist

	\item Thesis: Constrained learning and inference~(Advisor: Alejandro Ribeiro).

	\CVlistend



\CVsubheading{Polytechnic School of the University of São Paulo---Brazil}{2012--2015}
\textit{M.Sc.\ in Electrical Engineering}

	\CVlist

	\item Dissertation: Combinations of Adaptive Filters (Advisor: C\'{a}ssio Guimar\~{a}es Lopes).

	\CVlistend


\CVsubheading{École Centrale de Lyon {\normalfont and} INSA-Lyon---France}{2009}
\textit{Undergraduate exchange student of the M.Sc.\ in Acoustics program}
\vspace{3pt}


\CVsubheading{Polytechnic School of the University of São Paulo---Brazil}{2006--2011}
\textit{B.Sc.\ in Electrical Engineering (Electronic Systems)}
\vspace{3pt}




%%%%%%%%%%%%%%%%%%%%%%
\CVheading{Research Experience}


\CVsubheading{Polytechnic School of the University of São Paulo---Brazil}{2015}
\textit{Electronic Systems Engineering Department}

	\CVlist

	\item
	Design and prototype of an open source microphone array for acoustic imaging~(\href{https://github.com/lfochamon/memsarray}{\textbf{GitHub}}).

	\CVlistend



\CVsubheading{Polytechnic School of the University of São Paulo---Brazil}{2010--2013}
\textit{Mechanical Engineering Department}

	\CVlist

	\item
	Responsible for designing and implementing the vibroacoustic system of a full-sized
	\textit{aircraft cabin simulator} in collaboration with EMBRAER~(Brazilian aeronautic industry).

%	\item
%	Contributions included novel \textit{equalization techniques}, \textit{acoustical design}, \textit{customized sensing solutions}, and \textit{statistical analyses} leading to a passenger comfort model.

	\CVlistend



\CVsubheading{%
Polytechnic School of the University of São Paulo---Brazil%
}{2009--2011}
\textit{Mechanical Engineering Department}

	\CVlist

	\item
	Student researcher in an auralization project with the \textit{Institut für Technische Akustik}, RWTH, Germany.

	\CVlistend



%%%%%%%%%%%%%%%%%%%%%%
\CVheading{Teaching/Mentoring}


\CVsubheading{Women in STEM}{2022}
\textit{Judge of the \href{http://envisionrc.com/}{\textbf{\emph{ENVISION research competition}}}}
\vspace{3pt}

\CVsubheading{University of Pennsylvania}{2018--2019}
\textit{Mentor for the research experience for undergraduate program \href{https://sunfest.seas.upenn.edu}{\textbf{\emph{SUNFEST}}}}
\vspace{3pt}


\CVsubheading{University of Pennsylvania}{2016--2020}
\textit{TA and lecturer for the Stochastic Processes and Signal Processing undergraduate courses.}
\vspace{3pt}


\CVsubheading{Polytechnic School of the University of São Paulo---Brazil}{2013--2014}
\textit{TA for the Stochastic Processes undergraduate course}

	\CVlist

	\item Created instructional videos that have accumulated over $450$~followers and $140.000$~views (\href{https://www.youtube.com/channel/UC6LuNe5OPNiggEBcaI6UrRA}{\textbf{Youtube}}---in Portuguese).

	\CVlistend


\CVsubheading{INSACAST Formation Continue---France}{2009}
\textit{Assistant instructor}

	\CVlist

	\item Taught undergraduate laboratories, certification workshops~(COFREND and Dassault Aviation), and developed tutorials on ultrasonic nondestructive testing of concrete.

	\CVlistend





%%%%%%%%%%%%%%%%%%%%%%
\CVheading{Awards \& Fellowships}

	\CVlist

	\item \textbf{2020}: Best student paper award at IEEE ICASSP 2020 for ``The empirical duality gap of constrained statistical learning.''

	\item \textbf{2020}: Best paper award at IEEE ICASSP 2020 for ``Better safe than sorry: Risk-aware nonlinear Bayesian estimation.''

	\item \textbf{2018}: Best Ph.D.\ colloquium award\\(Dept. of Electrical and Systems Engineering, University of Pennsylvania).

	\item \textbf{2018}: Good citizen award for services to the department\\(Dept. of Electrical and Systems Engineering, University of Pennsylvania).

	\item \textbf{2018}: Outstanding editorial board service (IEEE Transactions on Signal Processing).

	\item \textbf{2013}: IEEE Standard Education Committee grant.

	\item Travel grants to major conferences, such as ICASSP, CDC, NeurIPS, and USENIX NSDI.

	\CVlistend



%%%%%%%%%%%%%%%%%%%%%%
\CVheading{Invited Seminars}

	\CVlist
	\item \textbf{February 2023}: ELLIS/CIS Network Seminar (EPFL).

	\item \textbf{April 2022}: Young Investigators Lecture Series (Caltech).

	\item \textbf{January 2022}: Foundations of Data Science Institute (FODSI) retreat.

	\item \textbf{December 2021}: Deep Learning Theory Symposium (Simons Institute).

	\item \textbf{April 2021}: Microsoft Research.

	\item \textbf{March 2021}: Massachusetts Institute of Technology (MIT EECS).

	\item \textbf{February 2021}: Johns Hopkins Mathematical Institute for Data Science (MINDS).

	\item \textbf{February 2021}: Toyota Technological Institute at Chicago (TTIC).

	\CVlistend



%%%%%%%%%%%%%%%%%%%%%%
\CVheading{Academic Service}

\CVsubheading{Self-governance}{}
\CVlist
\item 10/2023--09/2027: General assembly of the Stuttgart Center for Simulation Science of the University of Stuttgart~(deputy member)
\item 05/2020--12/2020: Penn Engineering COVID-19 Research and Academic Safety Committee
\CVlistend
\vspace{3pt}

\CVsubheading{Reviewer/Referee}{}
\CVlist
\item IEEE Trans. on Signal Processing; IEEE Signal Processing Letters; IEEE Signal Processing Magazine; IEEE Journal of Selected Topics in Signal Processing; IEEE Trans. on Signal and Information Processing over Networks; IEEE Trans. on Automatic Control; IEEE Trans. on Control of Network Systems; and conferences, such as NeurIPS, ICML, ICASSP, CDC\dots
\CVlistend
\vspace{3pt}




%%%%%%%%%%%%%%%%%%%%%%
\CVheading{Professional Experience}


\CVsubheading{Statistical analyses consulting}{2010--2015}

	\CVlist

	\item
	\textit{Statistical consulting} for research projects in medicine, behavioral sciences, ergonomics, etc.

	\CVlistend


\CVsubheading{INSACAST Formation Continue---France}{2009}

	\CVlist

	\item
	\textit{Consultant} in the design of a crack detection system for Saint-Gobain.

	\CVlistend


\CVsubheading{National Institute for Space Research~(INPE)---Brazil}{2004}

	\CVlist

	\item
	\textit{Laboratory assistant} of the \textit{Satellite Power Supply Group}. Participated in solar cells tests, project revisions, and \emph{power budget negotiations} with Chinese delegations.

	\CVlistend


%%%%%%%%%%%%%%%%%%%%%%
\CVheading{Languages}
	\vspace{-2pt}
	\CVlist

	\item
	Fluent in \textit{English}~(TOEFL iBT: 114), \textit{French}, and \textit{Portuguese}.

	\CVlistend




%%%%%%%%%%%%%%%%%%%%%%
%\CVheading{Technical Skills}
%
%\CVsubheading{Software}{}
%
%	\CVlist
%
%	\item $> 10$ years of experience with low level programming, DSP, and embedded systems.
%	\item Programming: MATLAB/Octave, R, Python, C, C++, and Lua.
%
%	\CVlistend
%
%
%\CVsubheading{Hardware}{}
%
%	\CVlist
%
%	\item $7$ years of experience with acoustical design and electronics for audio signal processing.
%	\item Printed circuit board design and assembly~(mixed signals, signal integrity).
%	\item Sensing and signal conditioning systems, digital hardware development, and FPGA.
%
%	\CVlistend

%\newpage


%%%%%%%%%%%%%%%%%%%%%%
% PUBLICATIONS AND OTHER TECHNICAL PRODUCTIONS
\nocite{*}


\CVheading{Publications~(\href{http://scholar.google.ca/citations?user=FIm-l-sAAAAJ}{Google scholar})}

\vspace*{-6pt}
\CVheading{Preprints}
\vspace*{-8pt}
\printbibliography[heading=none, resetnumbers=true, keyword=preprint]

\vspace*{-9pt}
\CVheading{Patents}
\vspace*{-8pt}
\printbibliography[heading=none, resetnumbers=true, keyword=patent]

\vspace*{-9pt}
\CVheading{Journals}
\vspace*{-8pt}
\printbibliography[heading=none, resetnumbers=true, keyword=journal]

\vspace*{-9pt}
\CVheading{ML \& Systems Conferences}
\vspace*{-8pt}
\printbibliography[heading=none, resetnumbers=true, keyword=conf_ml]

\vspace*{-9pt}
\CVheading{Control Conferences}
\vspace*{-8pt}
\printbibliography[heading=none, resetnumbers=true, keyword=conf_control]

\vspace*{-9pt}
\CVheading{Signal Processing Conferences}
\vspace*{-8pt}
\printbibliography[heading=none, resetnumbers=true, keyword=conf_sp]



\end{document}



%%%%%%%%%%%%%%%%%%%%%%%%
% GENERAL RESUME NOTES %
%%%%%%%%%%%%%%%%%%%%%%%%

http://www.youtube.com/watch?v=_0fjkKCsM1w

Avoid at all cost any of this buzz words and expressions:

- Results-oriented professional
- Cross-functional teams
- More than [x] years of progressively responsible experience
- Superior communication skills
- Strong work ethic
- Met or exceeded expectations
- Proven track record of success
- Works well with all levels of staff
- Team player
- Bottom-line orientation
- Extensive experience (abused in North America)
- Innovative (abused in Europe)
- Motivated
- Results-oriented
- Dynamic (used a lot in Brazil)
- Proven track record
- Team player
- Fast-paced
- Problem solver
- Entrepreneurial

Need to brush up on the skills section?  Here are some really good ideas:

- Communication: The ability to express and interpret ideas and convey knowledge.
Skills like speaking effectively, writing concisely, listening attentively, expressing ideas,
reporting information, editing, interviewing, and facilitating group discussion.

- Research and Planning: The ability to search for specific knowledge and formulate a
program for a definite course of action. Skills like forecasting, predicting, identifying
issues, finding alternatives, gathering information, solving problems, setting goals,
extracting information, and developing strategies.

- Human Relations: The ability to apply interpersonal skills to resolve conflict, relate to
people, and help people. Skills like providing support for others, listening, delegating
with respect, representing others, asserting, developing rapport, and perceiving
feelings.

- Management, Organization, Leadership: The ability to supervise others and guide
individuals and groups towards the completion of tasks. Skills like managing groups,
selling ideas, making decisions, managing conflict, coordinating tasks, teaching,
enlisting help.
